Watch Out for the Bully! Job Interference Study on Dragonfly Network

### 2016-04-09 related_work.tex
tweak in Conclustion and Related work
tweak in Related Work

The impact of job placement on both systems and applications has been the subject of many studies~\cite{dskinner,abhinav-sc13,jose-ipdps15}. We focus on the HPC-centric studies here. Skinner et al.\ identified significant performance variability due to network contention.~\cite{dskinner}. They found that performance variability is inevitable on either torus or fat-tree networks when network sharing among concurrently running applications is allowed.
%\TODO{what kind of system?}. 
Bhatele et al.\ studied the performance variability of a specific application, p3FD, running on different HPC production systems with torus network topologies \cite{abhinav-sc13}. They obtained performance consistency in their application when network resources were allocated compactly and exclusively and wide variability otherwise. Jokanovic et al. studied the impact of job placement to the workload and claimed that the key to reduce performance variability is to avoid network sharing~\cite{jose-ipdps15}.

@@

Our work complements the literature in the following ways. First, our simulations are driven by real application traces intended to be representative of production-scale application patterns. Second, we holistically examine behavior at both the overall system level as well as the application level, though we do not consider communication-pattern specific application mappings as Bogdan et al.\ did. Third, with the CODES simulation toolkit and related network models~\cite{codes, codes-dragonfly},  
%\TODO{cite codes, Misbah's dragonfly work}, 
we are able to simulate and examine system and application behavior at a very fine grain, collecting data at the dragonfly link level with packet-level fidelity. We believe these differences allowed us to uncover the ``bullying'' behavior, which to our knowledge is unreported in the literature. However, in a sense, Bogdan et al.'s work suggests these types of behaviors as possibilities deriving from the balance-first design rationale for the dragonfly.

>>>>

The impact of job placement on system behavior and application performance has been the subject of many studies.
%~\cite{dskinner,abhinav-sc13,jose-ipdps15}. 
We focus on the HPC-centric studies here. Skinner et al.\ identified significant performance variability due to network contention.~\cite{dskinner}. They found that performance variability is inevitable on either torus or fat-tree networks when network sharing among concurrently running applications is allowed.
%\TODO{what kind of system?}. 
Bhatele et al.\ studied the performance variability of a specific application, p3FD, running on different HPC production systems with torus network topologies \cite{abhinav-sc13}. They obtained performance consistency in their application when network resources were allocated compactly and exclusively and wide variability otherwise. Jokanovic et al. studied the impact of job placement to the workload and claimed that the key to reduce performance variability is to avoid network sharing~\cite{jose-ipdps15}.

@@

Our work complements the literature in the following aspects. First, our simulations are driven by real application traces intended to be representative of production-scale application patterns. Second, we holistically examine network behavior at both the overall system level as well as the individual application level, though we do not consider communication-pattern specific application mappings as Bogdan et al.\ did. Third, with the CODES simulation toolkit and related network models~\cite{codes, codes-dragonfly},  
%\TODO{cite codes, Misbah's dragonfly work}, 
we are able to simulate and examine system and application behavior at a very fine grain, collecting data at the dragonfly link level with packet-level fidelity. We believe these differences allowed us to uncover the ``bully'' behavior, which to our knowledge is unreported in the literature. However, in a sense, Bogdan et al.'s work suggests these types of behaviors as possibilities deriving from the balance-first design rationale for the dragonfly.
